|

### 2024-06-28 inst/MyArticle/PosterBioconductor.Rmd
update vignettes to work with latest version of prolfqua

```{r LFQData, echo=FALSE, fig.cap="Class Diagram for LFQData and related objects. The LFQData_Plotter class uses the LFQData class to implement methods for plotting.", out.width = '90%'}
knitr::include_graphics("LFQData_UML_V2.png")
```

@@

```{r ContrastUML, echo=FALSE, fig.cap="(ref:ContrastUML)", out.width = '90%'}
knitr::include_graphics("ContrastClassesUML.png")
```

@@

```{r prepro,  echo = TRUE , fig.cap="(ref:scaling)", out.width = '90%'}
library(prolfqua)
d <- prolfqua_data('data_ionstar')$filtered()
lfqd <- prolfqua::LFQData$new(d$data, d$config) 
t <- lfqd$get_Transformer()
lfqd <-  t$log2()$robscale()$lfq
pl <- lfqd$get_Plotter()
p_1 <- pl$intensity_distribution_density() +
  labs(tag = "A") + theme(legend.position = "none")
agr <- lfqd$get_Aggregator()
lfqp <- agr$medpolish()
p_2 <- agr$plot()$plots[[1]] + labs(tag = "B")
p_3 <- lfqp$get_Stats()$violin() + labs(tag = "C")
pl <- lfqp$get_Plotter()
p_4 <- pl$boxplots()$boxplot[[1]] + labs(tag = "D")
ggpubr::ggarrange(p_1, p_2, p_3, p_4)
```

@@

```{r}
allBenchmarks <- readRDS("../../inst/Benchresults/allBenchmarks.RDS")
benchmark_msstats <- readRDS("../../inst/Benchresults/benchmark_msstats.RDS")
msFragger <- readRDS(file = "../../inst/Benchresults/MSFragger_medpol_benchmark.RDS")

>>>>

```{r LFQData, echo=FALSE, fig.cap="Class Diagram for LFQData and related objects. The LFQData_Plotter class uses the LFQData class to implement methods for plotting.", out.width = '90%'}
knitr::include_graphics("graphics/LFQData_UML_V2.png")
```

@@

```{r ContrastUML, echo=FALSE, fig.cap="(ref:ContrastUML)", out.width = '90%'}
knitr::include_graphics("graphics/ContrastClassesUML.png")
```

@@

```{r prepro,  echo = TRUE , fig.cap="(ref:scaling)", out.width = '90%'}
library(prolfqua)
d <- prolfqua_data('data_ionstar')$filtered()
lfqd <- prolfqua::LFQData$new(d$data, d$config)

t <- lfqd$get_Transformer()
lfqd <-  t$log2()$robscale()$lfq
pl <- lfqd$get_Plotter()
p_1 <- pl$intensity_distribution_density() +
  labs(tag = "A") + theme(legend.position = "none")
agr <- lfqd$get_Aggregator()
lfqp <- agr$medpolish()
p_2 <- agr$plot()$plots[[1]] + labs(tag = "B")
p_3 <- lfqp$get_Stats()$violin() + labs(tag = "C")
pl <- lfqp$get_Plotter()
p_4 <- pl$boxplots()$boxplot[[1]] + labs(tag = "D")
ggpubr::ggarrange(p_1, p_2, p_3, p_4)
```

@@

```{r}
allBenchmarks <- readRDS(file.path("../../inst/Benchresults/",format( Sys.Date(), "%Y%m%d"),"allBenchmarks.RDS"))
benchmark_msstats <- readRDS(file.path("../../inst/Benchresults/",format( Sys.Date(), "%Y%m%d"),"benchmark_msstats.RDS"))
msFragger <- readRDS(file = file.path("../../inst/Benchresults/",format( Sys.Date(), "%Y%m%d"),"MSFragger_medpol_benchmark.RDS"))

### 2024-06-28 inst/MyArticle/SIB.Rmd
update vignettes to work with latest version of prolfqua

```{r readBenchmarkData}
getpath <- function(filN){
    f1 <- paste0("../../inst/Benchresults/",filN)
    if(f1 == ""){
       f1 <- system.file("Benchresults",filN,
                         package = "prolfquabenchmark")
    }
    return(f1)
}
allBenchmarks <- readRDS(getpath("allBenchmarks.RDS"))
benchmark_msstats <- readRDS(getpath("benchmark_msstats.RDS"))
benchmark_prodA <- readRDS(getpath("benchmark_medpolish_proDA.RDS"))
msFragger <- readRDS(getpath("MSFragger_medpol_benchmark.RDS"))

>>>>

```{r readBenchmarkData}
getpath <- function(filN){
    f1 <- file.path("../../inst/Benchresults/",format( Sys.Date(), "%Y%m%d"),filN)
    if (f1 == "") {
        f1 <- system.file("Benchresults",format( Sys.Date(), "%Y%m%d"),filN, package = "prolfquabenchmark")
    }
    message(f1)
    return(f1)
}
allBenchmarks <- readRDS(getpath("allBenchmarks.RDS"))
benchmark_msstats <- readRDS(getpath("benchmark_msstats.RDS"))
benchmark_prodA <- readRDS(getpath("benchmark_medpolish_proDA.RDS"))
msFragger <- readRDS(getpath("MSFragger_medpol_benchmark.RDS"))

### 2024-06-28 inst/MyArticle/analysingDataStartingfromProteinGroups.Rmd
update vignettes to work with latest version of prolfqua

TODO(wew,jg): Can you please add a oneliner of the purpose of the vignette?

@@

```{r anovaPvaluePlots, fig.cap="p-value distributions for ANOVA analysis."}
mod$anova_histogram(what = "FDR.Pr..F.")
```

@@

```{r anovaAnalysis}
ANOVA <- mod$get_anova()
ANOVA |>
  dplyr::filter(factor == "f1.:f2.") |>
  dplyr::arrange(FDR.Pr..F.) |>
  head(5)

ANOVA$factor |> unique()
protIntSig <- ANOVA |> dplyr::filter(factor == "f1.") |>
  dplyr::filter(FDR.Pr..F. < 0.25)

>>>>

TODO(wew,jg): Can you please add a one liner of the purpose of the vignette?

@@

```{r anovaPvaluePlots, fig.cap="p-value distributions for ANOVA analysis."}
mod$anova_histogram(what = "FDR")
```

@@

```{r anovaAnalysis}
ANOVA <- mod$get_anova()
ANOVA |>
  dplyr::filter(factor == "f1.:f2.") |>
  dplyr::arrange(FDR) |>
  head(5)

ANOVA$factor |> unique()
protIntSig <- ANOVA |> dplyr::filter(factor == "f1.") |>
  dplyr::filter(FDR < 0.25)

### 2024-06-28 inst/MyArticle/paper.Rmd
update vignettes to work with latest version of prolfqua

## read MQ peptide.txt and annotation table
startdata <- prolfqua::tidyMQ_Peptides(system.file(
  "samples/maxquant_txt/tiny2.zip", package = "prolfqua"))
annot <- readxl::read_xlsx(system.file(
  "samples/maxquant_txt/annotation_Ionstar2018_PXD003881.xlsx", package = "prolfqua"))
startdata <- dplyr::inner_join(annot, startdata, by = "raw.file")

@@

getpath <- function(filN){
    f1 <- paste0("../../inst/Benchresults/",filN)
    if (f1 == "") {
        f1 <- system.file("Benchresults",filN, package = "prolfquabenchmark")
    }
    message(f1)
    return(f1)
}
allBenchmarks <- readRDS(getpath("allBenchmarks.RDS"))
benchmark_msstats <- readRDS(getpath("benchmark_msstats.RDS"))
benchmark_prodA <- readRDS(getpath("benchmark_medpolish_proDA.RDS"))
msFragger <- readRDS(getpath("MSFragger_medpol_benchmark.RDS"))
benchmark_msqrob <- readRDS(getpath("benchmark_msqrob.RDS"))

>>>>

## read MQ peptide.txt and annotation table
startdata <- prolfquapp::tidyMQ_Peptides(system.file(
  "samples/maxquant_txt/tiny2.zip", package = "prolfqua"))
annot <- readxl::read_xlsx(system.file(
  "samples/maxquant_txt/annotation_Ionstar2018_PXD003881.xlsx", package = "prolfqua"))
startdata <- dplyr::inner_join(annot, startdata, by = "raw.file")

@@

getpath <- function(filN){
    f1 <- file.path("../../inst/Benchresults/",format( Sys.Date(), "%Y%m%d"),filN)
    if (f1 == "") {
        f1 <- system.file("Benchresults",format( Sys.Date(), "%Y%m%d"),filN, package = "prolfquabenchmark")
    }
    message(f1)
    return(f1)
}
allBenchmarks <- readRDS(getpath("allBenchmarks.RDS"))
benchmark_msstats <- readRDS(getpath("benchmark_msstats.RDS"))
benchmark_prodA <- readRDS(getpath("benchmark_medpolish_proDA.RDS"))
msFragger <- readRDS(getpath("MSFragger_medpol_benchmark.RDS"))
benchmark_msqrob <- readRDS(getpath("benchmark_msqrob.RDS"))

### 2024-06-28 inst/MyArticle/prolfqua_supplement.Rmd
update vignettes to work with latest version of prolfqua

```{r}
getpath <- function(filN){
    f1 <- paste0("../../inst/Benchresults/",filN)
    if (f1 == "") {
        f1 <- system.file("Benchresults",filN, package = "prolfquabenchmark")
    }
    message(f1)
    return(f1)
}
CPTACBenchmarks <- readRDS(getpath("CPTAC_Benchmark.RDS"))
mrob <- CPTACBenchmarks$benchmark_msqrob$pAUC_summaries()$ftable$content
mrob$package <- "msqrob2"
proda <- CPTACBenchmarks$benchmark_proDA$pAUC_summaries()$ftable$content
proda$package <- "proDA"
prolfqua <- CPTACBenchmarks$benchmark_merged$pAUC_summaries()$ftable$content
prolfqua$package <- "prolfqua"

@@

mqdata$data <- prolfqua::tidyMQ_Peptides(inputMQfile)
mqdata$config <- prolfqua::create_config_MQ_peptide()
annotation <- readxl::read_xlsx(inputAnnotation)
res <- prolfqua::add_annotation(
  mqdata$data,
  annotation,
  fileName = "raw.file"
)
mqdata$config$table$factors[["dilution."]] = "sample"
mqdata$config$table$factors[["run_Id"]] = "run_ID"
mqdata$config$table$factorDepth <- 1
mqdata$data <- prolfqua::setup_analysis(res, mqdata$config)
lfqdata <- prolfqua::LFQData$new(mqdata$data, mqdata$config)
lfqdata$data <- lfqdata$data |> 
  dplyr::filter(dilution. == "a" | dilution. =="c")
lfqdata$remove_small_intensities()
bb <- lfqdata$get_Plotter()
bb$missigness_histogram()
```

>>>>

```{r}
getpath <- function(filN){
    f1 <- file.path("../../inst/Benchresults/",format( Sys.Date(), "%Y%m%d"),filN)
    if (f1 == "") {
        f1 <- system.file("Benchresults",format( Sys.Date(), "%Y%m%d"),filN, package = "prolfquabenchmark")
    }
    message(f1)
    return(f1)
}
CPTACBenchmarks <- readRDS(getpath("CPTAC_Benchmark.RDS"))
mrob <- CPTACBenchmarks$benchmark_msqrob$pAUC_summaries()$ftable$content
mrob$package <- "msqrob2"
proda <- CPTACBenchmarks$benchmark_proDA$pAUC_summaries()$ftable$content
proda$package <- "proDA"
prolfqua <- CPTACBenchmarks$benchmark_merged$pAUC_summaries()$ftable$content
prolfqua$package <- "prolfqua"

@@

mqdata$data <- prolfquapp::tidyMQ_Peptides(inputMQfile)
mqdata$config <- prolfqua::create_config_MQ_peptide()
annotation <- readxl::read_xlsx(inputAnnotation)
res <- prolfquapp::add_annotation(
  mqdata$data,
  annotation,
  fileName = "raw.file"
)
mqdata$config$table$factors[["dilution."]] = "sample"
mqdata$config$table$factors[["run_Id"]] = "run_ID"
mqdata$config$table$factorDepth <- 1
mqdata$data <- prolfqua::setup_analysis(res, mqdata$config)
lfqdata <- prolfqua::LFQData$new(mqdata$data, mqdata$config)
lfqdata$data <- lfqdata$data |> 
  dplyr::filter(dilution. == "a" | dilution. =="c")
lfqdata$remove_small_intensities()
bb <- lfqdata$get_Plotter()
bb$missigness_histogram()
```
